A parametric system for adaptive extrusion width contour parallel toolpath generation

### 2019-08-14 6_validation.tex
Juns related work & Tims renaming of beading strategies

\paragraph{Naive Strategy}
We can define a beading strategy which emulates the naive method by disabling the marking of edges, so that we never employ transitioning.
\begin{align*}
\alpha_\text{max} &= \SI{180}{\degree} \\
b^-(d) &= 2 \left\lfloor \frac{d}{ 2w_\text{pref}} + \frac12 \right\rfloor \\
W(n,d)_i &= w_\text{pref} \text{ for all } i 
%\\
%L(n,d)_i &= w_\text{pref} \left(i + \frac12 \right) \text{ for all } i < \frac12 n
\end{align*}

\paragraph{Only outer bead}
We can emulate the method by \citeauthor{Moesen2011} by carefully choosing how the beading strategy functions deal with the outermost bead.
Also we turn off the reduction of line segments near 3-way intersections, so that the polygonal toolpaths emulate the remaining area to be filled by another path planning technique similar to their technique.

@@

\paragraph{Deviating center}
We can emulate the method by \citeauthor{Jin2017JMS}, by transcribing how they deviate from the naive tool paths.
We therefore base the beading strategy on the bead count $b^(d)$ defined by the naive beading strategy.
\citeauthor{Jin2017JMS} replace two beads from the naive toolpaths by a single one when the radius between the center and either of those beads falls short of $r_\text{min} = 0.8 w_\text{pref}$.
Conversely, they place an extra bead when the radius between the center and either of the innermost beads exceeds $r_\text{max} = 1.25 w_\text{pref}$.\cite{Jin2017JMS}
We emulate the rounded polygonal path rerouting they define by supplying a transition length which results in a discretized version of the rounded polygon segment.

@@

\paragraph{Inward distributed strategy}
For example, we can choose 
$$M(n,d)_i = \max(0, 1 - \frac{1}{N^2} (i - (n-1)/2)^2 )$$
to distribute the discrepancy over the innermost $2N$ beads, and distribute most of it to the inner beads.
That way we limit the region of impact of the distributed strategy to a central region and have the nominal bead width $w_\text{pref}$ in regions farther away.
This limits the impact of transitioning regions so that transitions keep the toolpaths smooth farther away from the central regions. % and it forces most of the beads to have exactly the prefered width.
Moreover, the bead widths equal the nominal bead width for large regions meaning that mechanial properties derived for prints using hte naive strategy will still hold approximately.

>>>>

\paragraph{Naive Beading Strategy}
We can define a beading strategy which emulates the naive method by disabling the marking of edges, so that we never employ transitioning.
\begin{align*}
\alpha_\text{max} &= \SI{180}{\degree} \\
b^-(d) &= 2 \left\lfloor \frac{d}{ 2w_\text{pref}} + \frac12 \right\rfloor \\
W(n,d)_i &= w_\text{pref} \text{ for all } i 
%\\
%L(n,d)_i &= w_\text{pref} \left(i + \frac12 \right) \text{ for all } i < \frac12 n
\end{align*}

\paragraph{Outer bead}
We can emulate the method by \citeauthor{Moesen2011} by carefully choosing how the beading strategy functions deal with the outermost bead.
Also we turn off the reduction of line segments near 3-way intersections, so that the polygonal toolpaths emulate the remaining area to be filled by another path planning technique similar to their technique.

@@

\paragraph{Centered}
We can emulate the method by \citeauthor{Jin2017JMS}, by transcribing how they deviate from the naive tool paths.
We therefore base the beading strategy on the bead count $b^(d)$ defined by the naive beading strategy.
\citeauthor{Jin2017JMS} replace two beads from the naive toolpaths by a single one when the radius between the center and either of those beads falls short of $r_\text{min} = 0.8 w_\text{pref}$.
Conversely, they place an extra bead when the radius between the center and either of the innermost beads exceeds $r_\text{max} = 1.25 w_\text{pref}$.\cite{Jin2017JMS}
We emulate the rounded polygonal path rerouting they define by supplying a transition length which results in a discretized version of the rounded polygon segment.

@@

\paragraph{Inward distributed}
For example, we can choose 
$$M(n,d)_i = \max(0, 1 - \frac{1}{N^2} (i - (n-1)/2)^2 )$$
to distribute the discrepancy over the innermost $2N$ beads, and distribute most of it to the inner beads.
That way we limit the region of impact of the distributed strategy to a central region and have the nominal bead width $w_\text{pref}$ in regions farther away.
This limits the impact of transitioning regions so that transitions keep the toolpaths smooth farther away from the central regions. % and it forces most of the beads to have exactly the prefered width.
Moreover, the bead widths equal the nominal bead width for large regions meaning that mechanial properties derived for prints using hte naive strategy will still hold approximately.
